---
title: "Assignment 1.10"
author: "Gabrielle Carbonel"
date: "09/15/2023"
output:
  html_document:
    df_print: paged
subtitle: CPSC 292 Section 03 (Hansen
---

### Collaboration team: 

Record who you've worked on the assignment with here. 


## Assignment 1.10 -- Data Frames

```{r setup, include=FALSE}
# Do not alter this section of code!
knitr::opts_chunk$set(echo = TRUE)
```

Write a R code in each chunk (gray space) that provides answers to the following questions. If any questions need direct answers, give them in regular text space (white space).

### Question 1

*Create a data frame that has columns with three different data types.*

```{r}
data.frame (
  name = c("Jill", "Jack", "Bob"),
  Age = c(19, 20, 19),
  Vote = c(T,F,T))
```

### Question 2

*Load the data set chickwts, which is study on chick weights based on feed type.*

```{r}
chickwts
```

*Use it to answer the following questions:*

  a. *What is the mean weight of all the chicks in the study? How many chicks are in each feed group?*
  
```{r}
mean(chickwts$weight)
(chickwts$feed)


```
  
  b. *Create two separate vectors with all the weights of the chicks in the study and all the feeds in the study.*
  
```{r}
x<-(ChickWeight$weight)
y<-(chickwts$feed)
print(data)
print(x)
print(y)
```
  
  c. *Subset the data frame into a new object that represents only the weights of chicks fed on horsebean.*
  
```{r}
horsebeanchik <- subset(chickwts, feed == "horsebean", chickwts$feed == F)
print(horsebeanchik)

```

  d. *Repeat this subsetting into a new object for chicks fed on sunflower.*
  
```{r}
sunflowerchik <- subset(chickwts, feed=="sunflower", weight == F)
print(sunflowerchik)
```

### Question 4

*The following line of code does not work. Correct the error so that the code returns the mean weight of chicks fed soybean or linseed feed.*
```{r}
soybeanlinseedchik <- subset(chickwts, feed == "soybean")
mean(soybeanlinseedchik$weight)
```
I removed the brackets and |.


Turn in this RMD file.